Notes on Control Plane Inference

### 2021-05-28 inference.tex
polish

\begin{lemma}[Assume-Currying]
  \label{lem:assume-currying}
  For $b_1,b_2 \in \BExpr$, $\sigma : \Value \to \Row^*$,
  \[\forall \pkt. \denote{\assume {b_1\wedge b_2}}^\sigma \pkt = \denote{\assume {b_1};\assume {b_2}}^\sigma \pkt\]
\end{lemma}
\begin{proof}
  Let $b_1,b_2,\sigma, \pkt$ be arbitrary. Compute using the definitions of $\denote\cdot$ and $\models$.
  \[\begin{array}{ll}
  \denote{\assume {b_1 \wedge b_2}}^\sigma \pkt \\
  = \{\pkt \mid \pkt \models b_1 \wedge b_2\} \\
  = \{\pkt \mid \pkt \models b_1, \pkt \models b_2\} \\
  = {\denote{\assume{b_1}}^\sigma}^\dagger\{\pkt \mid \pkt \models b_1\} \\
  = \denote{\assume{b_1}; \assume{b_2}}^\sigma \pkt
  \end{array}\]
\end{proof}

\begin{lemma}[Products and Sums]
  \label{lem:prod-sum}
  For $c_1,c_2, c_3 \in \Cmd$, $\sigma : \Value \to \Row^*$, $\pkt \in \Pkt$.
  $\denote{c_1;(c_2 \choice c_3)}^\sigma\pkt = \denote{c_1;c_2 \choice
    c_1;c_3}^\sigma\pkt$.
\end{lemma}
\begin{proof}
  Let $c_1,c_2,c_3$, $\sigma$, and $\pkt$ be given as above. Compute:
  \[
  \begin{array}{ll}
  \denote{c_1;(c_2 \choice c_3)}^\sigma \pkt \\
  = {\denote{c_2 \choice c_3}^\sigma}^\dagger\left(\denote{c_1}^\sigma\pkt\right) \\
  = {\denote{c_2}^\sigma}^\dagger\left(\denote{c_1}^\sigma \pkt\right)
  \cup {\denote{c_3}^\sigma}^\dagger\left(\denote{c_1}^\sigma \pkt\right) \\
  = {\denote{c_1;c_2}^\sigma}\pkt\cup {\denote{c_1;c_3}^\sigma}\pkt
  \end{array}
  \]
\end{proof}

@@

\begin{proof}
  Let $\sigma : \State $, $y \in \Var$, and $\pkt \in \Pkt$ be given.
  Proceed by induction on $c$.
  \begin{enumerate}[align=left]
  \item[($c = x := e$)] Assume $y \not \in \fvs(x:=e)$, that is, $y \neq x$.
    Compute $\denote{x:=e}^\sigma \pkt = \{\pkt\{ x \mapsto \edenote e
    \pkt\}\}$. Observe that $\pkt\{ x \mapsto \edenote e \pkt\}(y) = \pkt(y)$
    since $y \neq x$. The result follows.

@@

\begin{lemma}[Set Pseudo-Parametricity]
  \label{lem:parametricity-set}
  For $c \in \Cmd$, $\sigma : \State$, $y \in \Var$, $\pkt \in \Pkt$, if $Y
  \subseteq \Var \setminus \fvs(c)$, then $\forall \pkt' \in \denote{c}^\sigma
  \pkt$, $\pkt'(y) = \pkt(y)$.
\end{lemma}

@@

\begin{lemma}[Unused Variable Noninterference]
  \label{lem:param-noninter}
  For $c \in \Cmd$, $\sigma : \State$, $\pkt \in \Pkt$,
  $v_1,v_2 \in \Value$, $y \in \Var \setminus \fvs(c)$,
  $\denote{c}^\sigma \pkt\{y \mapsto v\} =_{\Var \setminus \{y\}}\denote{c}^\sigma\pkt\{y \mapsto v\}$.
\end{lemma}

@@

\begin{lemma}[Unused Variable Set Noninterference]
  \label{lem:param-noninter-set}
  For $c \in \Cmd$, $\sigma : \State$, $\pkt \in \Pkt$,
  $V_1,V_2 \subseteq \Value$, $Y \subseteq \Var \setminus \fvs(c)$,
  $\denote{c}^\sigma \pkt\{Y \mapsto V_1\} =_{\Var \setminus Y}\denote{c}^\sigma\pkt\{Y \mapsto V_2\}$.
\end{lemma}

@@

\begin{theorem}[Table Substitution]
  \label{thm:subst}
  For every $c \in \Cmd$, well-formed state $\sigma : \Value \to \Row^*$, and
  packet $\pkt \in \Pkt$,
  \[\denote{c}^\sigma\pkt = \denote{c[\sigma]}\,\pkt\]
\end{theorem}
\begin{proof}
   Proceed by induction on the structure of $c$.
  \begin{enumerate}[align=left]
    \item[$(c = (x := e))$] Immediate, since $(x:=e)[\sigma] = (x:=e)$.

@@

\begin{figure}[htp]
  %% \begin{minipage}[t]{0.5\textwidth}
  %% \[\begin{array}{r >{\triangleq}cl}
  %% \multicolumn{3}{l}{(\cdot)\instr : \Cmd \to \Cmd} \\
  %% (h.f := e)\instr && h.f := e \\
  %% (\assume b)\instr && b \\
  %% (\assert b)\instr && \assert b\\
  %% (c_1;c_2)\instr && c_1\instr;c_2\instr\\
  %% (c_1 \choice c_2)\instr && c_1\instr \choice c_2\instr\\
  %% (\{c\})\instr && \{c\instr\}\\
  %% (t.\apply())\instr && \\
  %% \multicolumn{3}{r}{
  %%   \qquad
  %%   \begin{array}[t]{l} \displaystyle
  %%     \{ \\
  %%     \quad \havoc \rho;\\
  %%     \quad \assume \rho \in t; \\
  %%     \quad \assume \rho.\matches = t.\keys; \\
  %%     \quad \displaystyle \bigchoice_{i=0}^{|t.\action| -1}
  %%     \left(\begin{array}{l}
  %%       \assume \rho.\action = i;\\
  %%       t.\action[i](\rho.\data)
  %%     \end{array}\right)\\
  %%     \} \choice ( \\
  %%     \quad \assume \forall \rho. \rho \in t \Rightarrow \rho.\matches \neq t.\keys;\\
  %%     \quad \SKIP \\
  %%     )
  %%   \end{array}}
  %% \end{array}
  %% \]
  %% \end{minipage}\begin{minipage}[t]{0.45\textwidth}
\[\begin{array}{r >{\triangleq}cl}
  \multicolumn{3}{l}{(\cdot)\instr : \Cmd \to \Cmd} \\
  (h.f := e)\instr && h.f := e \\
  (\assume b)\instr && \assume b \\
  (\assert b)\instr && \assert b\\
  (c_1;c_2)\instr && c_1\instr;c_2\instr\\
  (c_1 \choice c_2)\instr && c_1\instr \choice c_2\instr\\
  (t.\apply())\instr &&\\
  \multicolumn{3}{l}{
    \qquad
    \begin{array}[t]{l} \displaystyle
      \assume t.\matchrow(\rho_t); \\
      \assume \gamma_t.\keys = t.\keys; \\
    \displaystyle \bigchoice_{i=0}^{|t.\action| -1}
    \left(\begin{array}{l}
      \assume \gamma_t.\miss = 0;\\
      \assume \rho_t.\action = i;\\
      \assume \gamma_t.\hitAction = \rho_t.\id;\\
      t.\action[i](\rho_t.\data)
    \end{array}\right)\\
    \choice (\assume \gamma_t.\miss = 1; \SKIP)  \\
  \end{array}}
  \end{array}
  \]
  \caption{Symbolic Table Instrumentation. For simplicity, we
    assume each action in a table has the same number (and types) of parameters}
  \label{fig:table-instrument}
\end{figure}

@@

\begin{lemma}[Symbolic State Distributes]
  \label{lem:sigma-distrib}
  For $\sigma : \Value \to \Row^*$, $T,T_1,T_2 \subseteq \Table$ such that $T = T_1 \subseteq T_2$,
  $\state\sigma_{T} \Leftrightarrow \state{\sigma}_{T_1}\wedge\state{\sigma}_{T_2}$
\end{lemma}

@@

\begin{lemma}[Symbolic State distributes over Sequence]
  \label{lem:sigma-distrib-seq}
  For $\sigma : \Value \to \Row^*$, $c_1,c_2 \in \Cmd$,
  $\state\sigma_{c_1;c_2} \Leftrightarrow \state{\sigma}_{c_1}\wedge\state{\sigma}_{c_2}$
\end{lemma}

@@

\begin{lemma}[Symbolic State Distributes Over Choice]
  \label{lem:sigma-distrib-choice}
  For $\sigma : \Value \to \Row^*$, $c_1,c_2 \in \Cmd$,
  $\state\sigma_{c_1 \choice c_2} \Leftrightarrow \state{\sigma}_{c_1}\wedge\state{\sigma}_{c_2}$
\end{lemma}

@@

\begin{samepage}
\begin{theorem}[Instrumentation Equivalence]
  \label{thm:instr-equiv}
  Given a set of variables $V \subseteq \Var$ that contains no ghost variables
  or symbolic variables. For every well-formed $c \in \Cmd$ such that $\fvs(c) \subseteq V$,
  well-formed state $\sigma : \Value \to \Row^*$, and packet $\pkt \in \Pkt$,
  where $T \supseteq \tables(c)$, $R \supseteq \{\rho_t \mid t \in T\}$, and $G \supseteq \{\gamma_t \mid t \in
  T\}$,

@@

\begin{proof}
  Proceed by induction on $c$.
  \begin{enumerate}[align=left]
  \item[$(c = x:=e)$] Immediate, since $R = \emptyset = G$, $\assume{\state\sigma}_{x:=e} = \TRUE$, and $(x:=e)\instr = (x:=e)$.
  \item[$(c = \havoc x)$] \textit{sim}.
  \item[$(c = \assume b)$] \textit{sim}.
  \item[$(c = \assert b)$] \textit{sim}.
  \item[$(c = c_1;c_2)$] Note that well-formedness implies $\tables(c_1) \cap
    \tables(c_2) = \emptyset$. Let $T_2 = \tables(c_2)$ and $T_1 = T \setminus
    T_2$. Let $R_2 = \{\rho_t.* \mid t \in T_2\}$ and $R_1 = R \setminus R_2$.
    Let $G_2 = \{\rho_t.* \mid t \in T_2\}$ and $G_1 = G \setminus G_2$. Compute
    as follows:
    \[\begin{array}{ll}
    \denote{\havoc {R \cup G}; \assume{\state\sigma_{T}};(c_1;c_2)\instr}\,\pkt
    & \\
    = \denote{\havoc{R\cup G}; \assume{\state\sigma_{T}}; c_1\instr;c_2\instr}\,\pkt
    & \text{definition of }(\cdot)\instr \\
    = \denote{\havoc{R\cup G}; \assume{\state\sigma_{T_1}};\assume{\state\sigma_{T_2}};c_1\instr;c_2\instr}\,\pkt
    & \text{By Lemmas~\ref{lem:sigma-distrib-seq} \&~\ref{lem:assume-currying}} \\
    = \denote{\havoc{R_1 \cup G_1}; \havoc{R_2 \cup G_2}; \assume{\state\sigma_{T_1}};\assume{\state\sigma_{T_2}};c_1\instr;c_2\instr}\,\pkt
    & \text{By definition } \\
    = \denote{\havoc{R_1\cup G_1}; \havoc{R_2 \cup G_2}; \assume{\state\sigma_{T_1}};c_1\instr;\assume{\state\sigma_{T_2}};c_2\instr}\,\pkt
    & \text{By Lemma~\ref{lem:disj-comm} and } \tables(c_1) \cap \tables(c_2) = \emptyset \\
    = \denote{(\havoc{R_1 \cup G_1}; \assume{\state\sigma_{T_1}};c_1\instr);
      (\havoc{R_2 \cup G_2};\assume{\state\sigma_{T_2}};c_2\instr)}\,\pkt
    & \text{By Lemma~\ref{lem:disj-comm} and } \tables(c_1) \cap \tables(c_2) = \emptyset\\
    = \denote{\havoc{R_2 \cup G_2};\assume{\state\sigma_{T_2}};c_2\instr}^\dagger
    \left(\denote{\havoc{R_1 \cup G_1}; \assume{\state\sigma_{T_1}};c_1\instr}\,\pkt\right)
    & \text{by definition} \\
    =_V {\denote{c_2}^\sigma}^\dagger \left(\denote{\havoc{R_1 \cup G_1}; \assume{\state\sigma_{T_1}};c_1\instr}\,\pkt\right)
    & \text{by IH}(c_2) \text{ since } \fvs(c_2) \subseteq \fvs(c_1;c_2) \subseteq V \\
    =_V {\denote{c_2}^\sigma}^\dagger \left({\denote{c_1}^\sigma}^\dagger\pkt\right)
    & \text{by IH}(c_1) \text{ since } \fvs(c_1) \subseteq \fvs(c_1;c_2) \subseteq V \\
    = \denote{c_1;c_2}^\sigma\pkt
    & \text{by definition of }\denote{-}^\sigma\\
    \end{array}\]

@@

  \item[$(c = c_1\choice c_2)$]
    \[\begin{array}{ll}
    \denote{\havoc{R \cup G};\assume{\state\sigma_{T}}; (c_1 \choice c_2)\instr}\,\pkt
    & \\
    = \denote{\havoc{R \cup G};\assume{\state\sigma_{T}}; (c_1\instr \choice c_2\instr)}\,\pkt
    & \text{by definition of }(\cdot)\instr\\
    %% = \denote{\havoc{R \cup G};\assume{\state\sigma_{T_1} \wedge \state\sigma_{T_2}}; (c_1\instr \choice c_2\instr)}\,\pkt
    %% & \text{By Lemma~\ref{lem:sigma-distrib-choice}}\\
    %% = \denote{\havoc{R \cup G};\assume{\state\sigma_{T_1}}; \assume{\state\sigma_{T_2}}; (c_1\instr  \choice   c_2\instr)}\,\pkt
    %% & \text{By Lemma~\ref{lem:assume-currying}}\\
    = \denote{\havoc{R \cup G};\assume{\state\sigma_{T}}; c_1\instr
      \choice \havoc{R \cup G};\assume{\state\sigma_{T}}; c_2\instr}\,\pkt
    & \text{By Lemma~\ref{lem:prod-sum}} \\
    %% = \denote{\havoc{R \cup G}; \assume{\state\sigma_{T_1}}; c_1\instr
    %%   \choice \havoc{R \cup G}; \assume{\state\sigma_{T_2}}; c_2\instr}\,\pkt
    %% & \text{BY UNUSED-VARIABLES -> TRIVIAL ASSUMPTIONS LEMMA} \\
    %% =_V \denote{\havoc{R_1 \cup G_1}; \assume{\state\sigma_{c_1}}; c_1\instr
    %%   \choice \havoc{R_2 \cup G_2}; \assume{\state\sigma_{c_2}}; c_2\instr}\,\pkt
    %% & \text{BY UNUSEDVARIABLE HAVOC ELIMINATION LEMMA } \\
    = \denote{\havoc{R \cup G}; \assume{\state\sigma_{T}}; c_1\instr}\,\pkt
    \cup \denote{\havoc{R \cup G}; \assume{\state\sigma_{T}}; c_2\instr}\,\pkt
    & \text{by definition of }\denote{\cdot} \\
    =_V \denote{c_1}^\sigma\pkt \cup \denote{\havoc{R \cup G}; \assume{\state\sigma_{T}}; c_2\instr}\,\pkt
    & \text{By IH}(c_1) \text{ since } \fvs(c_1) \subseteq \fvs(c_1 \choice c_2) \subseteq V, \tables(c_1) \subseteq T \\
    =_V \denote{c_1}^\sigma\pkt \cup \denote{c_2}^\sigma\pkt
    & \text{By IH}(c_2) \text{ since } \fvs(c_2) \subseteq \fvs(c_1 \choice c_2) \subseteq V, \tables(c_2) \subseteq T \\
    = \denote{c_1 \choice c_2}^\sigma\pkt
    & \text{by definition of }\denote{\cdot}^\sigma
    \end{array}
    \]

@@

\begin{quote}
  \textbf{Inference Problem.} Given a command $c \in \Cmd$, compute (the
  weakest) control plane formula $\varphi$ such that if, for a state $\sigma :
  \Value \to \Row^*$, the following formula is valid \[\state\sigma_c
  \Rightarrow \varphi,\] then \[\forall \pkt \in \Pkt.~ \denote{c}^\sigma\pkt \neq \error \]
\end{quote}

@@

\begin{quote}
  \textbf{Repair Problem.} Given a command $c \in \Cmd$, compute (the weakest)
  control plane formula $\varphi$, and a test $b$ such that for every
  packet $\pkt \in \Pkt$ and state $\sigma : \Value \to \Row^*$, if the
  following formula is valid
  \[\state\sigma_c \Rightarrow \varphi,\]
  then \[\denote{\assume b; c}^\sigma\pkt \neq \error \]
\end{quote}

>>>>

\begin{lemma}[Assume-Currying]
  \label{lem:assume-currying}
  For $b_1,b_2 \in \BExpr$, $\sigma \in \State$,
  \[\forall \pkt. \denote{\assume {b_1\wedge b_2}}^\sigma \pkt = \denote{\assume {b_1};\assume {b_2}}^\sigma \pkt\]
\end{lemma}
\begin{proof}
  Let $b_1,b_2,\sigma, \pkt$ be arbitrary. Compute using the definitions of $\denote\cdot$ and $\models$.
  \[\begin{array}{ll}
  \denote{\assume {b_1 \wedge b_2}}^\sigma \pkt \\
  = \{\pkt \mid \pkt \models b_1 \wedge b_2\} \\
  = \{\pkt \mid \pkt \models b_1, \pkt \models b_2\} \\
  = {\denote{\assume{b_1}}^\sigma}^\dagger\{\pkt \mid \pkt \models b_1\} \\
  = \denote{\assume{b_1}; \assume{b_2}}^\sigma \pkt
  \end{array}\]
\end{proof}

\begin{lemma}[Products and Sums]
  \label{lem:prod-sum}
  For $c_1,c_2, c_3 \in \Cmd$, $\sigma \in \State$, $\pkt \in \Pkt$.
  $\denote{c_1;(c_2 \choice c_3)}^\sigma\pkt = \denote{c_1;c_2 \choice
    c_1;c_3}^\sigma\pkt$.
\end{lemma}
\begin{proof}
  Let $c_1,c_2,c_3$, $\sigma$, and $\pkt$ be given as above. Compute:
  \[
  \begin{array}{ll}
  \denote{c_1;(c_2 \choice c_3)}^\sigma \pkt \\
  = {\denote{c_2 \choice c_3}^\sigma}^\dagger\left(\denote{c_1}^\sigma\pkt\right) \\
  = {\denote{c_2}^\sigma}^\dagger\left(\denote{c_1}^\sigma \pkt\right)
  \cup {\denote{c_3}^\sigma}^\dagger\left(\denote{c_1}^\sigma \pkt\right) \\
  = {\denote{c_1;c_2}^\sigma}\pkt\cup {\denote{c_1;c_3}^\sigma}\pkt
  \end{array}
  \]
\end{proof}

@@

\begin{proof}
  Let $\sigma \in \State $, $y \in \Var$, and $\pkt \in \Pkt$ be given.
  Proceed by induction on $c$.
  \begin{enumerate}[align=left]
  \item[($c = x := e$)] Assume $y \not \in \fvs(x:=e)$, that is, $y \neq x$.
    Compute $\denote{x:=e}^\sigma \pkt = \{\pkt\{ x \mapsto \edenote e
    \pkt\}\}$. Observe that $\pkt\{ x \mapsto \edenote e \pkt\}(y) = \pkt(y)$
    since $y \neq x$. The result follows.

@@

\begin{lemma}[Set Pseudo-Parametricity]
  \label{lem:parametricity-set}
  For $c \in \Cmd$, $\sigma \in \State$, $y \in \Var$, $\pkt \in \Pkt$, if $Y
  \subseteq \Var \setminus \fvs(c)$, then $\forall \pkt' \in \denote{c}^\sigma
  \pkt$, $\pkt'(y) = \pkt(y)$.
\end{lemma}

@@

\begin{lemma}[Unused Variable Noninterference]
  \label{lem:param-noninter}
  For $c \in \Cmd$, $\sigma \in \State$, $\pkt \in \Pkt$,
  $v_1,v_2 \in \Value$, $y \in \Var \setminus \fvs(c)$,
  $\denote{c}^\sigma \pkt\{y \mapsto v\} =_{\Var \setminus \{y\}}\denote{c}^\sigma\pkt\{y \mapsto v\}$.
\end{lemma}

@@

\begin{lemma}[Unused Variable Set Noninterference]
  \label{lem:param-noninter-set}
  For $c \in \Cmd$, $\sigma \in \State$, $\pkt \in \Pkt$,
  $V_1,V_2 \subseteq \Value$, $Y \subseteq \Var \setminus \fvs(c)$,
  $\denote{c}^\sigma \pkt\{Y \mapsto V_1\} =_{\Var \setminus Y}\denote{c}^\sigma\pkt\{Y \mapsto V_2\}$.
\end{lemma}

@@

\begin{theorem}[Table Substitution]
  \label{thm:subst}
  For every $c \in \Cmd$, well-formed state $\sigma \in \Value \to \Row^*$, and
  packet $\pkt \in \Pkt$,
  \[\denote{c}^\sigma\pkt = \denote{c[\sigma]}\,\pkt\]
\end{theorem}
\begin{proof}
   Proceed by induction on the structure of $c$.
  \begin{enumerate}[align=left]
    \item[$(c = (x := e))$] Immediate, since $(x:=e)[\sigma] = (x:=e)$.

@@

\begin{figure}[htp]
\[\begin{array}{r >{\triangleq}cl}
  \multicolumn{3}{l}{(\cdot)\instr : \Cmd \to \Cmd} \\
  (h.f := e)\instr && h.f := e \\
  (\assume b)\instr && \assume b \\
  (\assert b)\instr && \assert b\\
  (c_1;c_2)\instr && c_1\instr;c_2\instr\\
  (c_1 \choice c_2)\instr && c_1\instr \choice c_2\instr\\
  (t.\apply())\instr &&\\
  \multicolumn{3}{l}{
    \qquad
    \begin{array}[t]{l} \displaystyle
      \assume t.\matchrow(\rho_t); \\
      \assume \gamma_t.\keys = t.\keys; \\
    \displaystyle \bigchoice_{i=0}^{|t.\action| -1}
    \left(\begin{array}{l}
      \assume \gamma_t.\miss = 0;\\
      \assume \rho_t.\action = i;\\
      \assume \gamma_t.\hitAction = \rho_t.\id;\\
      t.\action[i](\rho_t.\data)
    \end{array}\right)\\
    \choice (\assume \gamma_t.\miss = 1; \SKIP)  \\
  \end{array}}
  \end{array}
  \]
  \caption{Symbolic Table Instrumentation. For simplicity, we
    assume each action in a table has the same number (and types) of parameters}
  \label{fig:table-instrument}
\end{figure}

@@

\begin{lemma}[Symbolic State Distributes]
  \label{lem:sigma-distrib}
  For $\sigma \in \State$, $T,T_1,T_2 \subseteq \Table$ such that $T = T_1 \subseteq T_2$,
  $\state\sigma_{T} \Leftrightarrow \state{\sigma}_{T_1}\wedge\state{\sigma}_{T_2}$
\end{lemma}

@@

\begin{lemma}[Symbolic State distributes over Sequence]
  \label{lem:sigma-distrib-seq}
  For $\sigma \in \State$, $c_1,c_2 \in \Cmd$,
  $\state\sigma_{c_1;c_2} \Leftrightarrow \state{\sigma}_{c_1}\wedge\state{\sigma}_{c_2}$
\end{lemma}

@@

\begin{lemma}[Symbolic State Distributes Over Choice]
  \label{lem:sigma-distrib-choice}
  For $\sigma \in \State$, $c_1,c_2 \in \Cmd$,
  $\state\sigma_{c_1 \choice c_2} \Leftrightarrow \state{\sigma}_{c_1}\wedge\state{\sigma}_{c_2}$
\end{lemma}

@@

The following theorem relates the instrumented program to a
formal encoding of the state map $\sigma$, written $\state\sigma_T$ for a set of
tables $T$. The full definition is in Figure~\ref{fig:state-encode}.

\begin{samepage}
\begin{theorem}[Instrumentation Equivalence]
  \label{thm:instr-equiv}
  Given a set of variables $V \subseteq \Var$ that contains no ghost variables
  or symbolic variables. For every well-formed $c \in \Cmd$ such that $\fvs(c) \subseteq V$,
  well-formed state $\sigma \in \State$, and packet $\pkt \in \Pkt$,
  where $T \supseteq \tables(c)$, $R \supseteq \{\rho_t \mid t \in T\}$, and $G \supseteq \{\gamma_t \mid t \in
  T\}$,

@@

\begin{proof}
  Proceed by induction on $c$.
  \begin{enumerate}[align=left]
  \item[$(c = x:=e)$] Immediate, since $R = \emptyset = G$, $\assume{\state\sigma}_{x:=e} = \TRUE$, and $(x:=e)\instr = (x:=e)$.
  \item[$(c = \havoc x)$] \textit{sim}.
  \item[$(c = \assume b)$] \textit{sim}.
  \item[$(c = \assert b)$] \textit{sim}.
  \item[$(c = c_1;c_2)$] Note that well-formedness implies $\tables(c_1) \cap
    \tables(c_2) = \emptyset$. Let $T_2 = \tables(c_2)$ and $T_1 = T \setminus
    T_2$. Let $R_2 = \{\rho_t.* \mid t \in T_2\}$ and $R_1 = R \setminus R_2$.
    Let $G_2 = \{\rho_t.* \mid t \in T_2\}$ and $G_1 = G \setminus G_2$. Compute
    as follows:
    \[\begin{array}{ll}
    \denote{\havoc {R \cup G}; \assume{\state\sigma_{T}};(c_1;c_2)\instr}\,\pkt
    & \\
    = \denote{\havoc{R\cup G}; \assume{\state\sigma_{T}}; c_1\instr;c_2\instr}\,\pkt
    & \text{definition of }(\cdot)\instr \\
    = \denote{\havoc{R\cup G}; \assume{\state\sigma_{T_1}};\assume{\state\sigma_{T_2}};c_1\instr;c_2\instr}\,\pkt
    & \text{By Lemmas~\ref{lem:sigma-distrib-seq} \&~\ref{lem:assume-currying}} \\
    = \denote{\havoc{R_1 \cup G_1}; \havoc{R_2 \cup G_2}; \assume{\state\sigma_{T_1}};\assume{\state\sigma_{T_2}};c_1\instr;c_2\instr}\,\pkt
    & \text{By definition } \\
    = \denote{\havoc{R_1\cup G_1}; \havoc{R_2 \cup G_2}; \assume{\state\sigma_{T_1}};c_1\instr;\assume{\state\sigma_{T_2}};c_2\instr}\,\pkt
    & \text{By Lemma~\ref{lem:disj-comm}}, \\ &\text{since } \tables(c_1) \cap \tables(c_2) = \emptyset \\
    = \denote{(\havoc{R_1 \cup G_1}; \assume{\state\sigma_{T_1}};c_1\instr);
      (\havoc{R_2 \cup G_2};\assume{\state\sigma_{T_2}};c_2\instr)}\,\pkt
    & \text{By Lemma~\ref{lem:disj-comm}}, \\ & \text{since } \tables(c_1) \cap \tables(c_2) = \emptyset\\
    = \denote{\havoc{R_2 \cup G_2};\assume{\state\sigma_{T_2}};c_2\instr}^\dagger
    \left(\denote{\havoc{R_1 \cup G_1}; \assume{\state\sigma_{T_1}};c_1\instr}\,\pkt\right)
    & \text{by definition} \\
    =_V {\denote{c_2}^\sigma}^\dagger \left(\denote{\havoc{R_1 \cup G_1}; \assume{\state\sigma_{T_1}};c_1\instr}\,\pkt\right)
    & \text{by IH}(c_2) \text{ since } \fvs(c_2) \subseteq \fvs(c_1;c_2) \subseteq V \\
    =_V {\denote{c_2}^\sigma}^\dagger \left({\denote{c_1}^\sigma}^\dagger\pkt\right)
    & \text{by IH}(c_1) \text{ since } \fvs(c_1) \subseteq \fvs(c_1;c_2) \subseteq V \\
    = \denote{c_1;c_2}^\sigma\pkt
    & \text{by definition of }\denote{-}^\sigma\\
    \end{array}\]

@@

  \item[$(c = c_1\choice c_2)$]
    \[\begin{array}{ll}
    \denote{\havoc{R \cup G};\assume{\state\sigma_{T}}; (c_1 \choice c_2)\instr}\,\pkt
    & \\
    = \denote{\havoc{R \cup G};\assume{\state\sigma_{T}}; (c_1\instr \choice c_2\instr)}\,\pkt
    & \text{by definition of }(\cdot)\instr\\
    = \denote{\havoc{R \cup G};\assume{\state\sigma_{T}}; c_1\instr
      \choice \havoc{R \cup G};\assume{\state\sigma_{T}}; c_2\instr}\,\pkt
    & \text{By Lemma~\ref{lem:prod-sum}} \\
    = \denote{\havoc{R \cup G}; \assume{\state\sigma_{T}}; c_1\instr}\,\pkt
    \cup \denote{\havoc{R \cup G}; \assume{\state\sigma_{T}}; c_2\instr}\,\pkt
    & \text{by definition of }\denote{\cdot} \\
    =_V \denote{c_1}^\sigma\pkt \cup \denote{\havoc{R \cup G}; \assume{\state\sigma_{T}}; c_2\instr}\,\pkt
    & \text{By IH}(c_1) \text{ since } \fvs(c_1) \subseteq \fvs(c_1 \choice c_2) \subseteq V, \\
    & \text{and }\tables(c_1) \subseteq T \\
    =_V \denote{c_1}^\sigma\pkt \cup \denote{c_2}^\sigma\pkt
    & \text{By IH}(c_2) \text{ since } \fvs(c_2) \subseteq \fvs(c_1 \choice c_2) \subseteq V,\\
    & \text{and }\tables(c_2) \subseteq T \\
    = \denote{c_1 \choice c_2}^\sigma\pkt
    & \text{by definition of }\denote{\cdot}^\sigma
    \end{array}
    \]

@@

\begin{quote}
  \textbf{Inference Problem.} Given a command $c \in \Cmd$, compute (the
  weakest) control plane formula $\varphi$ such that if, for a state $\sigma \in \State$, the following formula is valid \[\state\sigma_c
  \Rightarrow \varphi,\] then \[\forall \pkt \in \Pkt.~ \denote{c}^\sigma\pkt \neq \error \]
\end{quote}

@@

\begin{quote}
  \textbf{Repair Problem.} Given a command $c \in \Cmd$, compute (the weakest)
  control plane formula $\varphi$, and a test $b$ such that for every
  packet $\pkt \in \Pkt$ and state $\sigma  \in \State$, if the
  following formula is valid
  \[\state\sigma_c \Rightarrow \varphi,\]
  then \[\denote{\assume b; c}^\sigma\pkt \neq \error \]
\end{quote}
